% VLDB template version of 2020-03-05 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template
\documentclass[sigconf, nonacm]{acmart}
%% The following content must be adapted for the final version
% paper-specific

\usepackage{color}
\usepackage{enumitem}
\usepackage{float}
\usepackage{balance}% for  \balance command ON LAST PAGE  (only there!)
\usepackage{algorithm, algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{tabu}
\usepackage{balance}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subfigure}
%\usepackage{times}
\usepackage{stfloats}
\usepackage{url}
\usepackage{comment}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{flushend}

\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2020}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle}

%
\newtheorem{problem}{Problem}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newcommand{\Bo}[1]{{\color{red} Bo: #1}}

\newcommand{\QM}[1]{{\color{blue}{#1}}}
\newcommand{\REPORT}[1]{{\color{purple}{#1}}}

\newcommand{\D}{\mathcal{T}}
\newcommand{\V}{\mathsf{V}}
\newcommand{\oR}{\mathcal{R}}
\newcommand{\MU}{\mathsf{U}}
\newcommand{\vats}{\mathsf{VFGS}}
\newcommand{\rand}{\mathsf{RAND}}
\newcommand{\full}{\mathsf{FULL}}
\newcommand{\avats}{\mathsf{VFGS}^{+}}
\newcommand{\cavats}{\mathsf{VFGS}^{+}\mathsf{CE}}
\newcommand{\sz}{\textsf{Shenzhen}}
\newcommand{\pt}{\textsf{Porto}}
\newcommand{\trim}{\vspace{-2mm}}

\newcommand{\stitle}[1]{\vspace*{0.4em}\noindent{\bf #1:\/}}
\newcommand{\sstitle}[1]{\vspace*{0.4em}\noindent{\bf #1\/.}}


\newcommand{\squishlist}{
 \begin{list}{$\bullet$}
 { \setlength{\itemsep}{0pt}
   \setlength{\parsep}{3pt}
   \setlength{\topsep}{3pt}
   \setlength{\partopsep}{0pt}
   \setlength{\leftmargin}{1.2em}
   \setlength{\labelwidth}{1em}
   \setlength{\labelsep}{0.6em}
 }
}
\newcommand{\squishend}{
 \end{list}
}

\settopmatter{printfolios=true}



\begin{document}
\title{Visual Fidelity-Guaranteed Sampling for \\ Large-scale Trajectory Data Visualization}

%\author{Qiaomu Shen$^{*}$,\quad Chuan Yang$^{*}$,\quad Chaozu Zhang$^{*}$,\quad Dan Zeng$^{\dag}$, \quad Wei Zeng$^{\ddag}$, \quad Bo Tang$^{*}$}

\affiliation{
  \institution{Qiaomu Shen$^{\dag}$,\quad Chaozu Zhang$^{\dag}$,\quad Chuan Yang$^{\dag}$, \quad Xiao Yan$^{\dag}$, \quad Dan Zeng$^{\ddag}$, \quad Wei Zeng$^{\$}$, \quad Bo Tang$^{\dag}$}
  \institution{$^{\dag}$ Department of Computer Science and Engineering, Southern University of Science and Technology}
  \mbox{qshen@connect.ust.hk, \{11612732@mail,11712021@mail, tangb3@\}sustech.edu.cn} \\
  \institution{$^{\ddag}$ Electrical Engineering, Mathematics and Computer Science, University of Twente}
  \institution{$^{\$}$ Shenzhen Institutes of Advanced Technology, Chinese Academy of Sciences}
  \mbox{xyan@cse.cuhk.edu.hk, d.zeng@utwente.nl, zengwei81@gmail.com}
  %\email{{{11711004, 11712532, 11613015}@mail.,tangb3@}sustech.edu.cn}
  %\mbox{qshen@connect.ust.hk, \{11612732@mail,11712021@mail,tangb3@\}sustech.edu.cn, d.zeng@utwente.nl, zengwei81@gmail.com}
}

\renewcommand{\shortauthors}{Qiaomu Shen, et al.}
\renewcommand{\shorttitle}{Paper ID: 324}

%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Visualizing large-scale trajectory data is a core subroutine for many smart city applications, e.g., traffic management, urban planning, and route recommendation. The task is challenging due to high scalability requirement and severe visual clutter. Sampling can effectively mitigate both problems but may harm visual fidelity, i.e., generating visualizations that look different from the exact one. In this work, we propose sampling techniques that provide \textit{theoretically guaranteed visual fidelity} for large-scale trajectory data visualization. We first define a natural pixel-based \textit{fidelity loss function} to measure the difference between two visualizations. However, our analysis shows that it is NP-hard to sample a fixed-size subset of trajectories to minimize the loss function. Therefore, we then devise an approximate algorithm named \textit{$\vats$} with a suite of optimization techniques, which runs efficiently but still provides guaranteed fidelity loss. By taking data distribution and human perception characteristics into consideration, we further improve $\vats$ to an advanced algorithm named $\avats$ to tackle the visual clutter problem. Extensive experiments (i.e., case-, user-, and quantitative- studies) are also conducted on real-world trajectory datasets to verify the effectiveness and efficiency of our proposals.
%In addition, comprehensive user studies further illustrate the superiority of our proposals in various applications, e.g., traffic flow comparison, and reachable route inspection.
\end{abstract}

\maketitle

\trim \trim

\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\shortauthors. Visual Fidelity-Guaranteed Sampling for Large-scale Trajectory Data Visualization. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup

\trim \trim %\trim

\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

\input{sections/Introduction.tex}

\trim
\input{sections/RelatedWork.tex}

\input{sections/ProblemFormulation.tex}

\input{sections/ProblemSolving.tex}

\input{sections/Evaluation.tex}

\input{sections/ConclusionFutureWork.tex}



%\begin{acks}
% This work was supported by the [...] Research Fund of [...] (Number [...]). Additional funding was provided by [...] and [...]. We also thank [...] for contributing [...].
%\end{acks}


\bibliographystyle{ACM-Reference-Format}
\bibliography{ref}

\end{document}
\endinput
